The Environmental Dependence of Structures for Massive Galaxies from the Hyper Suprime-Cam Survey

### 2016-07-24 draft/draft_v0.tex
Minor update

% Packages
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage[usenames]{color}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\bibliographystyle{apj}
\input psfig.tex

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\etal{{\ et al.~}}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\it HST}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\pp{\parshape 2 0truein 6.1truein .3truein 5.5truein}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer\ }}
\def\redbcg{$\Lambda \ge 30$}
\def\nonbcg{$\Lambda < 30$}
\def\logms{$\log (M_{\star}/M_{\odot})$}
\def\logmh{$\log (M_{\mathrm{Halo}}/M_{\odot})$}

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\comment}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277-8583, Japan}
\altaffiltext{2}{Princeton University Observatory, 
    Peyton Hall, Princeton, NJ 08544, USA}
\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
    P.O.~Box 23-141, Taipei 10617, Taiwan}
\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

    \plan{Basica idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey....}
    \end{itemize}

@@

    All the magnitudes used here are in AB system (\addref).  
    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\Lambda}=0.7$.

@@

    The Subaru Strategic Program (SSP, \addref ) makes use of the new prime-focus 
    camera, the Hyper Suprime-Cam (HSC; \addref: Miyazaki\etal 2012), on the 8.2-m 
    Subaru telescope at Mauna Kea.  
    Taking advantage of the large field of view (FoV; 1.5 deg in diameter) of HSC, 
    this ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of 
    sky in 5 broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the 
    \texttt{WIDE} part in the next few years.  
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$ square of degree of sky in all 5-band to the required depth of 
    \texttt{WIDE} survey.  
    The regions covered by this release are overlapped with several previous 
    spectroscopic survey (e.g. SDSS/BOSS \addref; GAMA \addref).

    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
    Synoptic Survey Telescope (LSST) pipeline (\addref: Ivezic\etal 2008,
    Axelrod\etal 2010), modified for use with Suprime-Cam and Hyper Suprime-Cam.  
    \texttt{hscPipe} first bias subtract, flat field, model background, and 
    perform object detection and measurement on the single exposure data. 
    Then, different exposures are warped onto a common World Coordinate System 
    (WCS) and combined into final images with improved signal-to-noise ratio 
    (SNR) after astrometric and photometric calibration.  
    The pixel scale of the combined images is 0.168$\arcsec$.
    The photometric calibration is based on data obtained from the Panoramic 
    Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\addref: Schlafly\etal 2012, Tonry\etal 2012, Magnier\etal 2013). 
    To achieve consistent deblending and photometry across all bands, the 
    \texttt{hscPipe} will perform multi-band post-processing on the combined 
    images.  
    The footprints and peaks of detected sources on each band will be 
    merged into a single catalog.    
    This consistent set of peaks and footprints is used as starting point 
    for deblend and measure objects on the combined images of each band.  
    These measurements are then merged into a reference catalog. 
    After fixing the centroids, shape, and other non-amplitude parameters 
    of every object in this catalog, \texttt{hscPipe} will derive forced 
    photometry measurements at each band. 
    Details of \texttt{hscPipe} and the multi-band processing method will 
    be presented in \addref (Bosch\etal 2017?).

@@

\subsection{Massive central galaxies in different environments}

@@

    To achieve this goal, we will select \logms$ > 11.5$ massive central 
    galaxies within host halo mass larger and smaller than \logmh$= 14.0$
    at $0.2 < z < 0.5$.  
    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function 
    are still quite uncertain at \logms$ > 11.5$, it is of great interest to 
    investigate the structure of galaxies in this region carefully.
    And, this stellar mass cut can greatly reduce the contamination of 
    satellites (e.g. \addref: van~Uitert\etal 2016).  
    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc 
    at redshit 0.2 and 0.5.  
    Hence, our redshift bin enables us to reliable measure the total stellar 
    mass within the inner 5 to 10 kpc (where the ``in-situ'' component should 
    still dominates) of massive galaxies at the high redshift end assuming the
    typical seeing of data. 
    At the same time, the depth of the data still allows to study the very 
    outskirt ($\sim 100$ kpc) of these galaxies at $z\sim 0.5$.  
    Also, such limits on mass and redshift ensure us a sizable sample while let 
    us safely ignore any significant structural evolution (no star formation, 
    lower merger rate \etal. e.g. \addref).

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ 
    relation (e.g. \addref), above \logms$ = 11.5$, there is a large scatter 
    of halo mass at fixed stellar mass.  
    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small 
    groups; while at \logmh$>14.0$, they start to become the centrals of very 
    massive groups and galaxy clusters.   
    Limited by the sample size and the capability of measureing halo mass for 
    individual central galaxy, we will simply separate the sample into two 
    broad halo mass bins with the help of the \redm cluster catalog 
    \footnote{See: http://risa.stanford.edu/redmapper/} (
    \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014; Rozo\etal 2015b).
    These clusters are selected from the SDSS DR8 photometric data 
    using overdensity of red-sequence galaxies. 
    For each cluster, the catalog provides robust estimations of 
    photometric redshift $z_{\Lambda}$ and richness $\Lambda$, along with 
    the best candidate of the central galaxy (the one with the highest 
    central probability \texttt{P\_CEN}).
    Information about the identified member candidates is also provided 
    separately. 
    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the 
    performance of the \redm cluster catalog.      
    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; 
    Simet\etal 2016) have tried to calibrate the $M_{200c}-\Lambda$ relation 
    using different methods.
    Despite the slightly different calibrations derived, it is safe to 
    assume that most clusters identified by \redm ($\Lambda > 20$) have
    $\log (M_{200c}/M_{\odot}) \geq 14.0$.  
    Considering the typical uncertainty of richness, and the fact that 
    \redm catalog starts to become incomplete toward low richness 
    ($\Lambda < 40$) end at $z > 0.33$, we will focus on the $\Lambda > 30$
    clusters in this work.  
    Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
    such richness cut gives us haloes with 
    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
    Therefore, \redm can provide us a sample of massive central galaxies in
    \logmh$\geq 14.0$ haloes.  
    And, we assume that, in the same footprints and redshift range, the 
    \logms$\geq 11.5$ galaxies outside \redm clusters are most likely to be 
    the central of \logmh$< 14.0$ haloes.

    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$
    galaxies should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    Ignoring the tiny difference in response curves between SDSS and HSC 
    $i$-band filters, we started by selecting all galaxies with 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered 
    in all five filters, and have already reached the expected depth of 
    \texttt{WIDE} survey.  
    The details of the HSC \texttt{cModel} photometry, and its performence
    will be described in Bosch\etal in. prep. 
    It is quite similar to the SDSS \texttt{cModel} in principle as it also 
    fits the total flux of an object using a combination of de~Vaucouleur 
    and exponential components after the PSF convolution is considered.  
    In our selection, we require well defined centroids and \texttt{cModel} 
    magnitude in all five bands. 
    \song{Should we discuss the impact of failed cModel photometry?}
    A series of quality control cuts are applied to remove objects that are 
    affected by saturation, cosmic ray, other optical artefacts.  
    After these cuts, a total number of \plan{N1} galaxies left in the 
    sample () \todo{Finish this part}  
    (This sample will be referred as \texttt{phoAll}).

    We match this sample with the central galaxies of \redm catalogs using 
    a $2.0\arcsec$ radius, and it results in \plan{N2} galaxies.  
    A small fraction of \redm centrals in the our footprints do not have 
    matched object in our sample due to severe contamination from optical 
    artefacts or bleeding trails from saturated objects.  
    And slight change of the mathcing radius has no impact of this sample.  
    For galaxy in this sample (will be referred as \texttt{redBCG}), 
    the photometric redshift of the cluster is available for each of them; 
    while for \plan of them, the spectroscopic redshift from SDSS DR8 is 
    also provided by \redm catalog when available.

    For the vast majority of galaxies that are not the centrals of very massive
    haloes, we need other sources for their redshfit estimations. 
    Although there has been many efforts for deriving photometric redshift 
    (photo-$z$) using HSC five-band photometry, it is still a working progress 
    now, and its performence at $z \leq 0.5$ is expected to be less satisfying 
    due to the lack of information at the shorter wavelength side of the 
    4000$\AA$ break.  
    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$)
    for this work.  
    The HSC database compiles a catalog of external spec-$z$ for this data 
    release by matching the detected objects with public data of several 
    spectroscopic surveys (e.g. SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref;
    \etal). 
    Duplicated matches from different sources are merged through interal 
    matching using $0.5\arcsec$ radius.

    We match the \texttt{phoAll} sample with this external spec-$z$ catalog 
    using a $1.0 \arcsec$ radius, and it leads to \plan{N3} results. 
    There are \plan{N4} objects at $0.2 \leq z \leq 0.5$.   
    The \texttt{redBCG} sample is also matched in the same way. 
    For ...
    \todo{Finish it...}

    \plan{Selection of the \texttt{PHOTO} sample}
    \begin{itemize}
        \item \plan{\texttt{PRIMARY} detection: In the inner region of the \texttt{Tract}
            and \textt{Patch}; has no \texttt{CHILD}.}
        \item \plan{Require the galaxy to be detected in all 5-band}
        \item \plan{For $i$-band detection, we require the object is covered by at least 
            4 \texttt{Visit}.}
        \item \plan{Has useful \texttt{cModel} photometry in all 5-band}
        \item \plan{$i$-band \texttt{cModel} magnitude brigther than 21.0 mag (justify this 
            later}
        \item \plan{Has to be extended object.}
        \item \plan{Has reliable central position and shape using SDSS algorithm}
        \item \plan{Typical quality cuts in $griz$-band.}
    \end{itemize}

    \plan{Selection of the \texttt{SPECZ} sample}
    \begin{itemize}
        \item \plan{Brief summary of the HSC spec-z catalog.}
        \item \plan{Internal catalog match results in 121998 galaxies}
        \item \plan{Brief break down of the spec-z sample; Most of the spectroscopic 
            redshift come from SDSS/BOSS and GAMA survey}
        \item \plan{Only keep objects at $z < 0.6$} \todo{Justify this later}
    \end{itemize}

\subsection{Central galaxies of $\Lambda > 20$ haloes using the \redm clusters}

    To select the central galaxies of cluster-level dark matter haloes, we make use of the 
    \redm cluster catalog \footnote{See: http://risa.stanford.edu/redmapper/}.

    \plan{Match to the \redm catalog}
    \begin{itemize}
        \item \plan{For this work, we use the \redm catalog based on SDSS DR8 
            photometry.} \todo{Need some explanation}
        \item \plan{Match with the \texttt{PHOTO} sample using a 1.0$\arcsec$
            matching radius, results in 704 clusters. (Justify this matching radius)}
        \item \plan{Select the \redm clusters at $z < 0.6$.}
        \item \plan{There is a small population of central galaxies from \redm that
            are within the HSC footprint, but does not have matched photometry, 
            briefly explain them}
    \end{itemize}

@@

@@

%\begin{thebibliography}{}

  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26

%\end{thebibliography}{}

\bibliography{hsc_massive.bbl}
\bibliographystyle{apj}

@@

\end{document}

>>>>

% Packages
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage[usenames]{color}

% Package Settings
\bibliographystyle{apj}
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\input psfig.tex

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}~}
\def\redbcg{$\Lambda \ge 30$}
\def\nonbcg{$\Lambda < 30$}
\def\logms{$\log (M_{\star}/M_{\odot})$}
\def\logmh{$\log (M_{\mathrm{Halo}}/M_{\odot})$}

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
\altaffiltext{2}{Princeton University Observatory, 
    Peyton Hall, Princeton, NJ 08544, USA}
\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
    P.O.~Box 23--141, Taipei 10617, Taiwan}
\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

    \plan{Basica idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

@@

    All the magnitudes used here are in AB system (\addref), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\Lambda}=0.7$.

@@

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\addref: Miyazaki\etal 2012), on the 8.2-m Subaru
    telescope at Mauna Kea.  
    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
    part in the next few years.  
    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
    The regions covered by this release are overlapped with several previous spectroscopic
    survey (e.g. SDSS/BOSS \addref; GAMA \addref).

    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal~2008, Axelrod\etal 2010),
    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
    detection and measurement on the single exposure data. 
    Then, different exposures are warped onto a common World Coordinate System (WCS) and
    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
    and photometric calibration.  
    The pixel scale of the combined images is 0.168$\arcsec$.  The photometric calibration
    is based on data obtained from the Panoramic Survey Telescope and Rapid Response
    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012,
    Magnier\etal 2013). 
    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
    will perform multi-band post-processing on the combined images.  
    The footprints and peaks of detected sources on each band will be merged into a single
    catalog.    
    This consistent set of peaks and footprints is used as starting point for deblend and
    measure objects on the combined images of each band.  
    These measurements are then merged into a reference catalog.  After fixing the
    centroids, shape, and other non-amplitude parameters of every object in this catalog,
    \texttt{hscPipe} will derive forced photometry measurements at each band. 
    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
    \addref (Bosch\etal 2017?).

@@

\subsection{Massive Central Galaxies in Different Environments}

@@

    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
    host halo mass larger and smaller than \logmh$= 14.0$ at $0.2 < z < 0.5$.  
    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
    structure of galaxies in this region carefully.
    And, this stellar mass cut can greatly reduce the contamination of satellites (e.g.
    \addref: van~Uitert\etal 2016).  
    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc at redshit
    0.2 and 0.5.  
    Hence, our redshift bin enables us to reliable measure the total stellar mass within
    the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) of
    massive galaxies at the high redshift end assuming the typical seeing of data. 
    At the same time, the depth of the data still allows to study the very outskirt ($\sim
    100$ kpc) of these galaxies at $z\sim 0.5$.  Also, such limits on mass and redshift
    ensure us a sizable sample while let us safely ignore any significant structural
    evolution (no star formation, lower merger rate \etal e.g. \addref).

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation (e.g.
    \addref), above \logms$ = 11.5$, there is a large scatter of halo mass at fixed
    stellar mass.  
    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small groups;
    while at \logmh$>14.0$, they start to become the centrals of very massive groups and
    galaxy clusters.   
    Limited by the sample size and the capability of measureing halo mass for individual
    central galaxy, we will simply separate the sample into two broad halo mass bins with
    the help of the \redm cluster catalog\footnote{See:
    http://risa.stanford.edu/redmapper/} ( \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014;
    Rozo\etal 2015b).
    These clusters are selected from the SDSS DR8 photometric data using overdensity of
    red-sequence galaxies. 
    For each cluster, the catalog provides robust estimations of photometric redshift
    $z_{\Lambda}$ and richness $\Lambda$, along with the best candidate of the central
    galaxy (the one with the highest central probability \texttt{P\_CEN}).
    Information about the identified member candidates is also provided separately. 
    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the performance of
    the \redm cluster catalog.      
    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; Simet\etal 2016)
    have tried to calibrate the $M_{200c}-\Lambda$ relation using different methods.
    Despite the slightly different calibrations derived, it is safe to assume that most
    clusters identified by \redm ($\Lambda > 20$) have $\log (M_{200c}/M_{\odot}) \geq
    14.0$.  
    Considering the typical uncertainty of richness, and the fact that \redm catalog
    starts to become incomplete toward low richness ($\Lambda < 40$) end at $z > 0.33$, we
    will focus on the $\Lambda > 30$ clusters in this work.  
    Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
    such richness cut gives us haloes with 
    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
    Therefore, \redm can provide us a sample of massive central galaxies in \logmh$\geq
    14.0$ haloes.  
    And, we assume that, in the same footprints and redshift range, the \logms$\geq 11.5$
    galaxies outside \redm clusters are most likely to be the central of \logmh$< 14.0$
    haloes.

    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$ galaxies
    should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.  Ignoring the tiny difference
    in response curves between SDSS and HSC $i$-band filters, we started by selecting all
    galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered in
    all five filters, and have already reached the expected depth of \texttt{WIDE} survey.  
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects
    The details of the HSC \texttt{cModel} photometry, and its performence will be
    described in \addref Bosch\etal in.\ prep. 
    It is quite similar to the SDSS \texttt{cModel} in principle as it also fits the total
    flux of an object using a combination of de~Vaucouleur and exponential components
    after the PSF convolution is considered.  
    For this work, we select objects that are classified as extended, have well defined 
    centroids, do not fail during the deblending process, and have \texttt{cModel} 
    magnitudes in all five bands. 
    \song{Should we discuss the impact of failed cModel photometry?} 
    A series of quality control cuts are applied to remove objects that are affected by 
    saturation, cosmic ray, other optical artefacts; and the ones that are too close to 
    the edge of the field in all five bands 
    (each criterion affects less than 8\% of the entire sample).
    After these cuts, a total number of 1760845 galaxies left in the sample.
    This sample will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    We match this sample with the central galaxies of \redm catalogs using a $1.0\arcsec$
    radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
    A small fraction of \redm centrals in the our footprints do not have matched object in
    our sample due to severe contamination from optical artefacts or bleeding trails from
    saturated objects.  
    And slight change of the mathcing radius has no impact of this sample.  
    For galaxy in this sample, the photometric redshift of the cluster is available for
    each of them; and for 72\% of them, the spectroscopic redshift from SDSS DR8 is also
    provided by \redm catalog when available. 
    This sample of will be referred as \texttt{redBCG} in the rest of the paper.

    For the vast majority of galaxies that are not the centrals of very massive haloes, we
    need other sources for their redshfit estimations. 
    Although there has been many efforts for deriving photometric redshift (photo-$z$)
    using HSC five-band photometry, it is still a working progress now, and its
    performence at $z \leq 0.5$ is expected to be less satisfying due to the lack of
    information at the shorter wavelength side of the 4000$\AA$ break.  
    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$) for this
    work.  
    The HSC database compiles a catalog of external spec-$z$ for this data release by
    matching the detected objects with public data of several spectroscopic surveys (e.g.
    SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref; \etal). 
    Duplicated matches from different sources are merged through interal matching using
    $0.5\arcsec$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs are 
    homogenized into a single flag that indicates whether the redshfit is secure, and 
    only secure spec-$z$ are used in this work. 
    %% This is catalog: "dr1_specz_use.fits"

    We match the \texttt{hscPho} sample with this external spec-$z$ catalog using a 
    $1.0 \arcsec$ radius, and it leads to 116813 matched objects.  
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among these matches, there are 42696 objects at $0.2 \leq z \leq 0.5$. 
    Most of these redshifts come from either SDSS or GAMA survey.
    To further exclude contamination from satellite galaxies, we aggressively remove 
    all galaxies that could be associated with the \redm clusters from this catalog.  
    First, the catalog of \texttt{redBCG} central galaxies is merged with the catalog  
    of their member galaxies. 
    Then, through cross matching using $1.0 \arcsec$ radius, all \texttt{hscPho} galaxies 
    that are within 2.5 Mpc of projected distance to any of cluster member are removed 
    from the catalog.  
    After this step, 29973 galaxies are left in the sample. 
    We will refer this sample as \texttt{nonBCG} later.
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

    The \texttt{redBCG} sample is also matched with external spec-$z$ catalog in the same
    way, and we update the redshift of the central galaxies with external spec-$z$ when 
    it is available.  
    For the unmatched ones, only 3 of them have spec-$z$ provided by the \redm catalog 
    (most likely due to different criteria during the selection of spec-$z$ sample).
    For the rest, we will use the photo-$z$ of the cluster from the \redm catalog instead.
    At $0.2 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
    sample. 
    Among them, 67 (17.9\%) of them do not have spec-$z$.
    Using the central galaxis have both spec- and photo-$z$, we estimate the median 
    absolute redshift difference $|z_{\mathrm{Photo}} - z_{\mathrm{Spec}}|$ is 
    $\sim 0.01$ (only 12 have absolute difference larger than 0.05; and the largest 
    difference is $\sim 0.12$).
    Such quality is good enough for the purpose of this work. 
    %% Saved as "dr1_redbcg_use_sed5b.fits"

\subsection{Stellar Masses from SED Fitting}

    To further select galaxies that are truly very massive central galaxies, we use 
    broadband Spectral Engergy Distributions (SEDs) fitting method (see \addref 
    Walcher\etal 2011 for a recent review) to derive stellar mass
    of our samples, and provide $k$-corrected photometry.

@@

  This research made use of 
  \href{http://www.astropy.org/}{Astropy}, a community-developed 
  core Python package for Astronomy (Astropy Collaboration, 2013; 
  \href{https://github.com/kbarbary/sep}{sep} 
  Source Extraction and Photometry in Python \citep{PythonSEP}.

@@

\bibliography{redbcg}

@@

\label{lastpage}
\end{document}
